Analysis paper

### 2021-06-17 analysis/analysis.Rmd
update plots

del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

@@

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

@@

# median performance
p_median <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

@@

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

@@

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

@@

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

@@

# bias
p_bias <- scores %>%
  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

@@

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

@@

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.9, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths)

>>>>

del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
del_cols <- c(del_cols, "coverage_deviation")
df[, (del_cols) := NULL]

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = FALSE, 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
del_cols <- c(del_cols, "coverage_deviation")
df[, (del_cols) := NULL]

@@

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = "Forecast horizon") + 
  theme_light()

@@

# median performance
p_median <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "median WIS", x = "Forecast horizon") + 
  theme_light()

@@

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "WIS - standard deviation", x = "Forecast horizon") + 
  theme_light()

@@

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "sharpness", x = "Forecast horizon") + 
  theme_light()

@@

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Absolute error", x = "Forecast horizon") + 
  theme_light()

@@

# bias
p_bias <- scores %>%
  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Bias", x = "Forecast horizon") + 
  theme_light()

@@

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Empirical coverage", x = "Forecast horizon") + 
  theme_light()

@@

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.9, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "empirical coverage", x = "Forecast horizon") + 
  theme_light()
